\documentclass{resume}

\begin{document}
\name{Chris Osborn, Ph.D.}
\contact
	{80 Parnassus Ave., San Francisco, CA 94117}
	{+1 (551) 427-5867}
	{chris.osborn@gmail.com}
\sites
	{https://www.linkedin.com/in/cbosborn}{LinkedIn}
	{http://www.cbo.is}{Personal}
	{https://www.github.com/cbosborn}{Github}
	{https://www.cache.ai}{Cache}
\section{Education}
	\jobtitle{Ph.D. Physics}
	\employerdates{Columbia University}{June, 2008 -- January, 2014}
	\begin{itemize}
	\item As the first graduate student in Dr. Tanya Zelevinsky's lab, I built a quantum physics experiment from the ground up: custom-built solid state diode lasers, optical systems \& RF control electronics, vacuum \& oven systems, metalworking, \& experimental control software.
	\item Transitioned from lab-building to first major results for publication in top research journals (see \textit{Papers \& Research}).
	\item With a passion for teaching \& communication, presented research at international conferences, trained the lab's second generation of graduate students, \& taught undergraduate courses extensively for the physics department.
	\note
		{Honors:}
		{National Science Foundation GRFP (honorable mention, 2010).}
	\end{itemize}

	\jobtitle{B.S. Physics$^{\dagger}$, B.S. Mathematics$^{\dagger}$}
	\employerdates{University of Rochester}{September, 2004 -- May, 2008}
	\begin{itemize}
		\item Active member of the physics department, as a teaching assistant for undergraduate labs, \& as a volunteer tutor, frequently tutoring after hours to accommodate demand.
		\note
			{Honors:}
			{Phi Beta Kappa National Honors Society (2008), Sigma Pi Sigma Physics Society (2007).}
	\end{itemize}
	\foot{$^{\dagger}$Magna Cum Laude}

\section{Papers \& Research}
	\begin{itemize}
	\pub
		{The Physics of Ultracold Sr$_2$ Molecules: Optical Production \& Precision Measurement}
		{http://academiccommons.columbia.edu/catalog/ac\%3A173488}
		{Ph.D. thesis}
	\pub
		{Nonadiabatic Effects in Ultracold Molecules via Anomalous Linear \& Quadratic Zeeman Shifts}
		{http://journals.aps.org/prl/abstract/10.1103/PhysRevLett.111.243003}
		{Physical Review Letters 111, 243003}
	\pub
		{Optical Production of Stable Ultracold $^{88}$Sr$_2$ Molecules}
		{http://journals.aps.org/prl/abstract/10.1103/PhysRevLett.109.115303}{Physical Review Letters 109, 115303}
	\pub
		{Dynamically Configurable \& Optimizable Zeeman Slower Using Permanent Magnets \& Servomotors}
		{http://www.opticsinfobase.org/josab/abstract.cfm?URI=josab-29-4-729&origin=search}
		{Journal of the Optical Society of America B, Volume 29 No. 4}
	\note
		{Undergraduate research:}
		{Dr. Nick Bigelow's atomic physics lab (Rochester, 2008), Dr. Gunter L{\"u}pke's condensed matter lab (William \& Mary, 2007), \& Dr. Lewis Rothberg's biophysics lab (Rochester, 2006)}
	\end{itemize}

\section{Work}
	\jobtitle{Founder, CEO}
	\employerdates{Cache Finance, Inc.}{January, 2015 -- July, 2016}
	\begin{itemize}
	\item Conceived an ambitious financial services vision for Cache, out of tools originally built in grad school to manage a student stipend in NYC.
	\item Engineered back end services: financial integration via \href{http://www.plaid.com}{Plaid}, REST API for client app \& interaction with numerous 3$^{\rm rd}$ party services. Written in JavaScript/Nodejs, \& deployed to the cloud with AWS EC2, AWS Lambda, Heroku, etc.
	\item Involved deeply in the formulation of the problems to be solved by the A.I. framework, \& in the ongoing process of tuning the algorithms to successfully detect patterns in users' spending.
	\item Engineered \& designed the entirety of the front end product(s): multiple early iterations of an iOS app (Swift \& Objective-C), \& then later an SMS assistant \& lightweight web app (Angular, React, Twilio).
	\item Operated a 50-user private beta, iterating on feedback \& guiding the product from a budgeting tool to a proposal for a fully-fledged financial instrument.
	\item Managed all business operations \& fundraising efforts.
	\end{itemize}

\end{document}
